%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Competition}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Team Leader} % Role
    {2017 Service Design Competition} % Event
    {3rd place} % Location
    {Oct. 2017 - Dec. 2017} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {Conducted the field research to interview with users in order to capture the users' demands.}
        \item {Utilized design thinking methodology to rethink the service process and adopted several brainstorming techniques to come up with innovative ideas.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Team Leader} % Role
    {2018 Johnson \& Johnson x Listerine Business Competition - Bring Out the Bold} % Event
    {Finalist (5 out of 200)} % Location
    {Dec. 2017 - May 2018} % Date(s)
    {
      \begin{cvitems} % Description(s)
      	\item {Joined Listerine marketing campaign in Carrefour and observed customer behavior during trail to catch the customer insight.}
        \item {Designed and conducted a customer questionnaire survey and afterward applied simple logistic regression to identify which type of customer tending to purchase mouthwash and vice versa.}
        \item {Redesigned the marketing campaign with limited budget attracting more children to give it a shot and increasing the penetration rate of Listerine in the long run.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Team Leader} % Role
    {Financial Elite Camp for Youth} % Event
    {2nd place} % Location
    {Feb. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s)
      	\item {Proposed an investment portfolio within 18 hours to generate sufficient cash flow and matching family's wishes such as purchasing a new car at the same time.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
