%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Education \& Courses}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\cvsubsection{Education}


\begin{cventries}

%---------------------------------------------------------
  \cventry
    {M.S. in Technology Management, GPA: 4.12/ 4.3} % Degree
    {National Chung Hsing University} % Institution
    {Taichung, Taiwan} % Location
    {Sep. 2017 - Jun. 2019} % Date(s)
    {\begin{cvitems} % Description(s) bullet points
        \item {Theme of Dissertation: Identifying Emerging Trends of Blockchain Technology Using a Topic-based Patent Mining Model (ICIM 30th Nice paper award)}
      \end{cvitems}}
    
%---------------------------------------------------------
  \cventry
    {B.S. in Sociology with a minor in Business Administration} % Degree
    {National Sun Yat-sen University} % Institution
    {Koahsiung, Taiwan} % Location
    {Sep. 2013 - Jul. 2017} % Date(s)
    {}
    
%---------------------------------------------------------
\end{cventries}

%---------------------------------------------------------
\cvsubsection{Online Courses}

\begin{cvhonors}

%---------------------------------------------------------
  \cvhonor
    {} % Award
    {\href{https://www.datacamp.com/statement-of-accomplishment/track/d05bff099253e5f221288f01272b0afb6eb80e05}{SQL Fundamentals}} % Event
    {DataCamp} % Location
    {Nov. 2019} % Date(s)

%---------------------------------------------------------
  \cvhonor
    {} % Award
    {\href{https://www.coursera.org/account/accomplishments/specialization/certificate/JUYCQBR3TMVW?utm_medium=certificate&utm_source=link&utm_campaign=copybutton_certificate}{Tensorflow in Practice Specialization in deeplearning.ai}} % Event
    {Coursera} % Location
    {Nov. 2019} % Date(s)

%---------------------------------------------------------
  \cvhonor
    {} % Award
    {\href{https://www.coursera.org/account/accomplishments/specialization/certificate/TG88EP6ASTZ7?utm_medium=certificate&utm_source=link&utm_campaign=copybutton_certificate}{Deep Learning Specialization in deeplearning.ai}} % Event
    {Coursera} % Location
    {Jul. 2019} % Date(s)

%---------------------------------------------------------
  \cvhonor
    {} % Award
    {\href{https://www.coursera.org/account/accomplishments/certificate/T4ARKFWRSLB2?utm_medium=certificate&utm_source=link&utm_campaign=copybutton_certificate}{Machine Learning in Stanford Online}} % Event
    {Coursera} % Location
    {Jul. 2019} % Date(s)


%---------------------------------------------------------
  \cvhonor
    {} % Award
    {\href{https://www.datacamp.com/statement-of-accomplishment/track/a31b1837666595d34f5378a093df9fa2056e29e2}{Data Scientist with Python}} % Event
    {DataCamp} % Location
    {Jan. 2019} % Date(s)

%---------------------------------------------------------
  \cvhonor
    {} % Award
    {\href{https://www.datacamp.com/statement-of-accomplishment/track/dfdda8840e45bd7989991aa90b1287ed8fbbb872}{Data Scientist with R}} % Event
    {DataCamp} % Location
    {Dec. 2018} % Date(s)


%---------------------------------------------------------
\end{cvhonors}