%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Data Analyst Intern - Digital Management Department} % Job title
    {Cathay Securities Corp.} % Organization
    {Taipei, Taiwan} % Location
    {Jul. 2018 - Aug. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Summarized daily news including FinTech, AI, and Blockchain topics.}
        \item {Analyzed the current trends in trading market such as credit score, robo-advisor, etc.}
        \item {Integrated open data into customer identity information to calculate the credit limit and further established dashboard to visualize the result through Tableau.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Blockchain Content intern - Pocket Coin} % Job title
    {\href{http://pocketcoin.tw}{Starter Tech.}} % Organization
    {Taipei, Taiwan/ Remote} % Location
    {Feb. 2018 - Aug. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Translated crucial news, novelty applications and Blockchain fundamental concepts in plaint text.}
        \item {Introduced top 100 market value cryptocurrencies about their purpose and technical strategies.}
        \item {Developed the quantitative strategies using technical metrics and applied them to trade cryptocurrencies during the competition against the other interns.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Intern - International Business Department} % Job title
    {China Merchants Bank} % Organization
    {Guangzhou, China} % Location
    {Jul. 2017 - Aug. 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Classified the incoming telegram, and sent to the responsible person.}
        \item {Verified the document of L/C, including invoices, bill of lading, insurance forms, etc and further investigated the route of ship to avoid money laundering}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
